pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-01-29 article.tex
Show fig 2
Add fig 3
Added figure 4

% TODO: write script to create figure 2, see
% https://github.com/richelbilderbeek/pirouette/issues/37
The resulting figure is shown in figure 2.

\begin{figure}[h]
  \includegraphics[width=\textwidth]{figure_2.png}
\end{figure}

@@

% TODO: write script to create figure 3, see
% https://github.com/richelbilderbeek/pirouette/issues/38
The resulting figure is shown in figure 3.

@@

% TODO: write script to create figure 4, see
% https://github.com/richelbilderbeek/pirouette/issues/39
The resulting figure is shown in figure 4
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{pirouette resources}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The resulting figure is shown in figure 2.

\richel{Update figure 2 to use idealized tree}

\begin{figure}[h]
  \includegraphics[width=\textwidth]{figure_2.png}
  \caption{
    The error BEAST2 makes from a phylogeny using the same 
    diversification model as it was generated by
  }
\end{figure}

@@

The resulting figure is shown in figure 3.

\begin{figure}[h]
  \includegraphics[width=\textwidth]{figure_3.png}
  \caption{
    The error BEAST2 makes from a phylogeny when
    picking the best inference model
  }
\end{figure}

@@

The resulting figure is shown in figure 4

\begin{figure}[h]
  \includegraphics[width=\textwidth]{figure_4.png}
  \caption{
    The error BEAST2 makes from a phylogeny 
    picking the best inference model, compared to the background noise?
    Here, the twin column shows the error BEAST2 makes on an idealized
    tree, to measure the noise, which is the minimal error.
  }
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{pirouette resources}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
